\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[francais]{babel}
\usepackage[T1]{fontenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{makeidx}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{booktabs}
\usepackage{array}


\usepackage[left=1cm,right=1cm,top=3cm,bottom=2cm]{geometry}
\title{Note on the Quarterly Database}
\author{clément carrier}


\begin{document}
\maketitle

\section{Database}

In this file, I describe the database used, and explain in more details the transformation made before using them into our model. If not mentioned, variables are introduce for the 11 original members countries of the eurozone + Greece + Sweden + UK + Denmark.\\

All the variables in the folders /IMF, /ECB and /OECD contain .csv file corresponding to original (raw) database. We transform the variables thanks to the .R file called "transformation". Then we save subsets from the complete database according to the model that we want to estimate. 




\subsection{ECB}

These are the variables from ECB data warehouse originally in monthly frequency (I took the mean on each quarter) : 
\begin{itemize}
\item HICP : ICP.M.COUNTRY.N.000000.4.INX
\item Processed food exc. Alcohol and tobacco : ICP.M.COUNTRY.N.FDPXAT.4.INX
\item Unprocessed food	: ICP.M.COUNTRY.N.FOODUN.4.INX
\item Indus good exc. Energy : ICP.M.COUNTRY.N.IGXE00.4.INX
\item Energy	:	ICP.M.COUNTRY.N.NRGY00.4.INX
\item Services	:	ICP.M.COUNTRY.N.SERV00.4.INX
\item Unemployment : STS.M.COUNTRY.S.UNEH.RTT000.4.000
\end{itemize}

\vspace{0.5cm}

These variables are loaded directly from a file called ecbq.RData in the subfolder data/Quarterly/ECB. This file was built from the .R file used for the monthly frequency database. These variables are already transformed (log or /100), but not differentiated yet. The starting date is Q1 1990. \\

I also use in quarterly frequency : 

\begin{itemize}
\item Compensation per employee : $MNA.Q.N.COUNTRY.W2.S1.S1._Z.COM_PS._Z._T._Z.IX.V.N$
\item Exchange rate EUR/USD : EXR.Q.USD.EUR.SP00.A
\item Nominal Effective Exchange Rate : EXR.Q.E1.EUR.ERC0.A
\item GDP : $MNA.Q.N.COUNTRY.W2.S1.S1.B.B1GQ._Z._Z._Z.XDC.LR.N$
\item Productivity : $MNA.Q.N.COUNTRY.W0.S1.S1._Z.LPR_PS._Z._T._Z.IX.LR.N$
\item DowJones Euro Stoxx 50 index : FM.Q.U2.EUR.DS.EI.DJES50I.HSTA

\end{itemize}

\vspace{0.5cm}

These variables are in the folder Data/ECB and are raw variables directly loaded from the ECB database. These variables are transformed in the .R file called "traitementECB" located in the subfolder Data/ECB. (The transformation are describe in the following table) \\

Two databases are saved in the subfolder Data/ECB, one in level, the other one differentiated one time: 

\begin{itemize}
\item dfecbq.Rdata 
\item difdfecbq.RData 
\end{itemize}

\vspace{0.5cm}

The first one starts from Q1 1990, whereas the differentiated one starts from Q2 1990.





\subsection{IMF}

These are the variables from IMF (IFS) originaly in monthly frequency, but transformed into quarterly frequency :
\begin{itemize}
\item Commodity Prices, Crude Oil, Petroleum (World)
\item London Interbank Offer Rate, 3-Month (US)
\item Industrial Production
\item Interest Rates, Monetary Policy-Related Interest Rate, FPOLM (Eurozone + US)
\item Central Bank, Total Gross Assets (ECB + FED)
\end{itemize}

\vspace{0.5cm}



These are the variables from IMF (IFS) loaded in quarterly frequency :
\begin{itemize}
\item M1 (Eurozone)
\item M3 (Eurozone)
\item Producer Price, all comodities
\item GDP deflator 
\item Interest Rates, Money Market Rate (FED + ECB)
\end{itemize}

\vspace{0.5cm}

These variable are in the folder Data/Quarterly/IMF and are raw variable directly loaded from the IFS database. These variables are transformed in the .R file called "traitementIMF" located in the subfolder Data/Quarterly/IMF. (The transformation are describe in the following table) \\

Two databases are saved in the subfolder Data/Quarterly/IMF, one in level, the other one differentiated one time: 

\begin{itemize}
\item imf.Rdata 
\item difimf.RData 
\end{itemize}

\vspace{0.5cm}



The first one starts from Q1 1990, whereas the differentiated one starts from Q2 1990.






\subsection{OECD}




These are the variables from OECD :
\begin{itemize}
\item Short-term Interest rates (Monthly Monetary and Financial Statistics)
\item Long-term Interest rates (Monthly Monetary and Financial Statistics)
\end{itemize}

\vspace{0.5cm}

These variables are originaly in monthly frequency. They were transformed and saved when I built the monthly database. 




\section{Recapitulative table}


\begin{table}[h]
  \centering
  \caption{Database quarterly}
     \scalebox{0.6}{
    \begin{tabular}{crrrrrrrr}
    \toprule
    \multicolumn{9}{c}{Database}
      \\
    \midrule
    Concept &
      \multicolumn{1}{c}{Variables} &
      \multicolumn{1}{c}{Source} &
      Frequency  (original) &
      Frequency (transformed) &
      Adjustment &
      \multicolumn{1}{c}{Country} &
      \multicolumn{1}{c}{Original} &
      \multicolumn{1}{c}{Transformation}
      \\
      \midrule
    \multirow{10}[20]{*}{Price} &
      HICP  &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Processed food exc. Alcohol and tobacco &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Unprocessed food &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Indus good exc. Energy &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Energy &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Services &
      ECB &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      GDP deflator &
      IFS (IMF) &
      quarterly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      PPI (all commodities) &
      IFS (IMF) &
      quarterly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
      &
      &
      &
      &
      &
      &
      (exc. Luxemburg) &
      &
      
      \\
     &
      Oil Price &
      IFS (IMF) &
      monthly &
      quarterly &
      NSA/NWD  &
      World &
      index &
      log
      \\
     &
      Compensation per employee &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      index &
      log
      \\
      \midrule
    \multirow{4}[8]{*}{Economic Activity} &
      GDP (nominal) &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      by country &
      Millions EUR &
      log
      \\
     &
      Productivity &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      by country &
      index &
      log
      \\
     &
      Indus. Production &
      IFS (IMF) &
      monthly &
      quarterly &
      NSA &
      by country &
      index &
      log
      \\
     &
      Unemployment rate &
      ECB &
      monthly &
      quarterly &
      SA/NWD &
      by country &
      \% &
      /100
      \\
      \midrule
    \multirow{4}[8]{*}{Interest rates} &
      Short-term Interest rates &
      OECD &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      annual \% &
      /100
      \\
     &
      Long-term Interest rates &
      OECD &
      monthly &
      quarterly &
      NSA/NWD  &
      by country &
      annual \% &
      /100
      \\
     &
      Interest Rates, Money Market Rate &
      IFS (IMF) &
      quarterly &
      quarterly &
      NSA/NWD  &
      by country &
      annual \% &
      /100
      \\
     &
      LIBOR 3 month &
      IFS (IMF) &
      monthly &
      quarterly &
       &
      US &
      annual \% &
      /100
      \\
      \midrule
    \multirow{4}[8]{*}{Monetary} &
      M1 &
      IFS (IMF) &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      EUR &
       $*10^{-6}$ + log
      \\
     &
      M3 &
      IFS (IMF) &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      EUR &
      $*10^{-6}$ + log
      \\
     &
      Monetary Policy-Related Interest Rate &
      IFS (IMF) &
      monthly &
      quarterly &
      NSA/NWD  &
      US/EZ &
      annual \% &
      /100
      \\
     &
      Central Bank Asset &
      IFS (IMF) &
      monthly &
      quarterly &
      NSA/NWD  &
      US/EZ &
      USD/EUR &
      log
      \\
      \midrule
    \multirow{3}[6]{*}{Other} &
      NEER &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      index &
      log
      \\
     &
      EUR/USD exchange rate &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      index &
      -
      \\
     &
      DowJones Euro Stoxx 50 &
      ECB &
      quarterly &
      quarterly &
      NSA/NWD  &
      EZ &
      index &
      log
      \\
    \bottomrule
    \end{tabular}
    }
 \label{tab:addlabel}
\end{table}





\end{document}